\setupbodyfont[xits]
\setupinteraction[state=start]

\useURL [ms-font-install] [http://www.microsoft.com/typography/truetypeinstall.mspx] [] [Installing fonts on Windows]
\starttext

\section{Introduction}

XITS is Times-like font for scientific publishing with support for mathematical
typesetting. It has wide coverage of Latin, Greek and Cyrillic scripts, as
well as extensive coverage of Unicode symbols used in mathematics and other
fields of science. XITS supports also proper mathematical typesetting and can
be used to typeset complex mathematical equations in modern \TEX\ engines,
namely \LUATEX\ and \XETEX, as well as Microsoft Office starting from 2007
version.

XITS is available as an OpenType font, in four styles; regular, bold, italic
and bold italics, besides the maths font.

\section{Font features}

XITS supports the following OpenType features:

\starttable[|lT|l|]
\HL
\NC feature\NC Description \NC\SR
\HL
\NC \Use{2}[I]{All fonts} \MR
\NC kern \NC Kerning \NC\FR
\NC liga \NC Ligatures \NC\MR
\NC onum \NC Oldstyle numbers \NC\MR
\NC frac \NC Diagonal fractions \NC\MR
\NC \Use{2}[I]{The maths font, spports additional features} \MR
\NC ss01 \NC Mathematical Calligraphic Alphabet \NC\MR
\NC ss02 \NC Mathematical Greek Sans Serif Alphabet \NC\MR
\NC ss03 \NC Mathematical Italic Sans Serif Digits \NC\MR
\NC ss04 \NC Mathematical Bold Monospace Digits \NC\MR
\NC ss05 \NC Mathematical Bold Double-Struck Alphabet \NC\MR
\NC ss06 \NC Mathematical Italic Double-Struck Alphabet \NC\MR
\NC ss07 \NC Mathematical Bold Italic Double-Struck Alphabet \NC\MR
\NC ss08 \NC Upright Integrals \NC\LR
\NC ss09 \NC Negated Symbols With Vertical Stroke \NC\MR
\HL
\stoptable


\section{Installation}

\subsection{\CONTEXT}
\CONTEXT\ MkIV are needed for using the math font, text fonts can be used with
either MkIV or MkII with \XETEX\ engine, MkII with \PDFTEX\ is not supported.

Recent versions of \CONTEXT\ already have typescripts for XITS, so just
installing the fonts into TEXMF tree is enough.

\subsection{\LATEX}
A modern \TEX\ engine with Unicode and OpenType support is needed, namely
\LUATEX\ or \XETEX. In addition to {\ss fontspec} package, {\ss unicode-math}
is needed for using XITS fonts in math mode.

If you are using \LUATEX\ then you can either install the fonts OS wide or in
TEXMF tree. If you are using \XeTeX\ then you need to either install fonts OS
wide, or adapt your {\ss fontconfig} configuration to look for for fonts
installed under TEXMF tree, otherwise you will not be able to access fonts by
font name.

\subsection{MS Office}
MS Office 2007 or newer is required, please refer to Microsoft’s
\from[ms-font-install] for general font installation instruction.

\section{Usage}

\subsection{\LATEX}

\subsubsection{Examples}
\startTEX
\documentclass{article}
\usepackage{unicode-math}
\setmainfont{XITS}
\setmathfont{XITS Math}

\begin{document}
Text $x+y=\sqrt{z}$
\end{document}
\stopTEX

\subsection{\CONTEXT}

\subsubsection{Examples}

\startTEX
\setupbodyfont[xits]

\starttext
Text $x+y=\sqrt{z}$
\stoptext
\stopTEX

\stoptext
